Analysis

### 2023-03-01 Analysis.rmd
update performance table with standard deviations

@@

```{r, performance-table}
make_performance_table <- function(scores) {
  scores |>
    filter(scale %in% c("log", "natural")) |>
    summarise_scores(by = c("model", "target_type", "scale", "horizon")) |>
    filter(horizon == 2) |>
    select(model, target_type, scale, interval_score, coverage_50, coverage_90) |>
    pivot_wider(names_from = scale, values_from = interval_score) |>
    select(model, target_type, natural, log, coverage_50, coverage_90) |>
    mutate(across(c(where(is.numeric)), signif, digits = 2)) |>
    arrange(target_type, model) |>
    kable(format = "latex", booktabs = TRUE, 
          align = c("l", "l", rep("c", 4)),
          caption = "Performance for two-week-ahead forecasts \\label{tab:scores}",
          linesep = c('', '', '', '\\addlinespace'),
          col.names = c("Model", "Target", "WIS", "WIS (log scale)", 
                        "Coverage 50%", "Coverage 90%")) |> 
    kable_styling(latex_options = c("scale_down", 
                                    "hold_position")) 
}

scores |>
  filter(model %in% models_non_human) |>
  make_performance_table() |>
  cat(file = 'manuscript/performance-table.tex')

scores_revised |>
  filter(model %in% models_non_human) |>
  make_performance_table() |>
  cat(file = 'manuscript/performance-table-revised.tex')

scores_comparable_ensemble |>
  make_performance_table() |>
  cat(file = 'manuscript/performance-table-comparison-rt.tex')

>>>>

```{r}
scores_summarised <- scores |>
  filter(scale %in% c("log", "natural")) |>
  filter(model %in% models_non_human) |>
  summarise_scores(by = c("model", "target_type", "scale", "horizon", "forecast_date")) |>
  group_by(target_type, scale, horizon) |>
  # mutate(interval_score = (interval_score - mean(interval_score)) / sd(interval_score)) |>
  group_by(model, target_type, scale, horizon) |>
  summarise(mean = mean(interval_score), 
            sd = sd(interval_score)) |>
  pivot_wider(id_cols = c(model, target_type, horizon), 
              names_from = scale, values_from = c(mean, sd), names_prefix = "stand_") |>
  arrange(target_type, model)
```

@@

```{r, performance-table}
make_performance_table <- function(scores, scores_summarised, 
                                   hor = 2) {
  scores |>
    filter(scale %in% c("log", "natural")) |>
    summarise_scores(by = c("model", "target_type", "scale", "horizon")) |>
    select(model, target_type, scale, interval_score, coverage_50, coverage_90, horizon) |>
    pivot_wider(names_from = scale, values_from = interval_score) |>
    select(model, target_type, natural, log, coverage_50, coverage_90, horizon) |>
    inner_join(scores_summarised) |>
    mutate(across(c(where(is.numeric)), signif, digits = 2)) |>
    arrange(target_type, model) |>
    mutate(natural = label_fn(natural), 
           log = label_fn(log)) |>
    mutate(natural = paste0(natural, " (", label_fn(sd_stand_natural), ")"), 
           log = paste0(log, " (", label_fn(sd_stand_log), ")")) |>
    filter(horizon == hor) |>
    select(-mean_stand_log, -sd_stand_log, -mean_stand_natural, -sd_stand_natural, -horizon) |>
    kable(format = "latex", booktabs = TRUE, 
          align = c("l", "l", rep("c", 4)),
          caption = "Performance for two-week-ahead forecasts \\label{tab:scores}",
          linesep = c('', '', '', '\\addlinespace'),
          col.names = c("Model", "Target", "WIS", "WIS (log scale)", 
                        "Coverage 50%", "Coverage 90%")) |> 
    kable_styling(latex_options = c("scale_down", 
                                    "hold_position")) 
}

scores |>
  filter(model %in% models_non_human) |>
  make_performance_table(scores_summarised = scores_summarised) %>%
  gsub("\\{table\\}", "\\{table\\*\\}", x = .) |>
  cat(file = 'manuscript/performance-table.tex')

scores |>
  filter(model %in% models_non_human) |>
  make_performance_table(scores_summarised = scores_summarised, hor = 4) %>%
  gsub("\\{table\\}", "\\{table\\*\\}", x = .) |>
  cat(file = 'manuscript/performance-table-horizon-4.tex')

# scores_revised |>
#   filter(model %in% models_non_human) |>
#   make_performance_table() |>
#   cat(file = 'manuscript/performance-table-revised.tex')
# 
# 
# scores_comparable_ensemble |>
#   make_performance_table() |>
#   cat(file = 'manuscript/performance-table-comparison-rt.tex')
